\begin{resumo}[Abstract]
 \begin{otherlanguage*}{english}
   \textit{In recent years it has become increasingly common application development for end users through the development of robust spreadsheets, database queries, and even applications from specialized tools. This development method is called in the literature as End User Development (EUD). In the Brazilian federal government, a public agency has recognized these efforts by end users and adopted a development model for applications made under this modality, resulting in a high internal satisfaction. One of the specific characteristics of the EUD is flexibility in the development of these applications, which can lead developers to neglect standards and best software development practices. Given this context, the purpose of this work is to propose a development support solution (system) based on EUD within the public agency in question, contributing to improve the quality and maintainability of applications. The research is classified as qualitative, exploratory and applied. As a result there was the construction of the EUD-based development support system for the agency in question. With the work it was possible to verify that there is a need to support the EUD developer within the body, given the variety in the experience of the same and the standards and techniques used by different departments of the institution.}

   \vspace{\onelineskip}
 
   \noindent 
   \textit{\textbf{Key-words}: end user development. decentralized development. apex. application express.}
 \end{otherlanguage*}
\end{resumo}